### 2020-12-10 ctuth-names.tex
Adding of introduction part.

	xdoctype-SemPro .meta:n = {
		doctype-english = { Semestr ~ Project },
		doctype-czech = { Semestrální ~ projekt },
		doctype-slovak = { Semestrálne ~ projekt }
	},
	xdoctype-B .meta:n = {
		doctype-english = { Bachelor ~ Project },
		doctype-czech = { Bakalářská ~ práce },
		doctype-slovak = { Bakalárska ~ práca }
	},
	xdoctype-M .meta:n = {
		doctype-english = { Master ~ Thesis },
		doctype-czech = { Diplomová ~ práce },
		doctype-slovak = { Diplomová ~ práca }
	},
	xdoctype-D .meta:n = {
		doctype-english = { Dissertation ~ Thesis },
		doctype-czech = { Disertační ~ práce },
		doctype-slovak = { Dizertačná ~ práca }
	},

>>>>

	xdoctype-SemPro .meta:n = {
		doctype-english = { Semestr ~ Project },
		doctype-czech = { Semestrální ~ projekt },
		doctype-slovak = { Semestrálne ~ projekt }
	},
	xdoctype-SemProJakoM .meta:n = {
		doctype-english = { Semestr ~ Project ~ as ~ background ~ for ~ Master ~ Thesis},
		doctype-czech = { Semestrální ~ projekt ~ jako ~ podklad ~ pro ~ diplomovou ~ práci},
		doctype-slovak = { Semestrálne ~ projekt ~ ako ~ podklad ~ pre ~ diplomovú ~ prácu}
	},
	xdoctype-B .meta:n = {
		doctype-english = { Bachelor ~ Project },
		doctype-czech = { Bakalářská ~ práce },
		doctype-slovak = { Bakalárska ~ práca }
	},
	xdoctype-M .meta:n = {
		doctype-english = { Master ~ Thesis },
		doctype-czech = { Diplomová ~ práce },
		doctype-slovak = { Diplomová ~ práca }
	},
	xdoctype-D .meta:n = {
		doctype-english = { Dissertation ~ Thesis },
		doctype-czech = { Disertační ~ práce },
		doctype-slovak = { Dizertačná ~ práca }
	},
